Measuring Lattices

### 2023-02-28 MeasuringLattices_uv5016/MeasuringLattices.tex
Finished response to reviews and updated the tex file to show the changes

@@

In order to measure a meaningful distance between two objects, the objects need to
be placed in a ”metric space”. For crystallographic unit cells, this will often be a
vector space amenable to the tools and techniques of
linear algebra, at least locally. Because six free parameters are needed to define a unit
cell, the space will need to be at least six-dimensional. Depending on
other criteria, more dimensions may be needed; gluing the edges of
a manifold generates the need for more dimensions.

@@

	In working with a space in which there are 
	multiple symmetry-related occurrences of items of interest (atoms, molecules, or,
	in this case, unit cells), it is conventional to choose a fundamental
	region \cite{enwiki:1028832752}. In a two-dimensional graph, it would often be chosen as the all-plus
	quadrant. In crystallography, it might be a unit cell, a
	particular asymmetric unit of a crystal, or even a molecule.

@@

	The obvious step to find the shortest distance between two
	lattices is to simply compute the Euclidean distance between
	them in the fundamental unit. That distance might not be the
	shortest that can be found, but no geodesic could 
	be longer. It makes a useful starting point. Call 
	this distance $d_0$.

@@

\begin{figure}
		\includegraphics[width = 0.5\textwidth ]{4_3}
		\label{4_3}
	\caption{}
\end{figure}	
	It is clear that within the fundamental unit, ignoring all symmetry
	transforms and considering B and C, B is the atom closer to
	A. Draw a circle centered on A that touches B. We see that the
	circle crosses the boundary and a portion is outside of the
	fundamental unit. Any atom that is within that region outside the fundamental unit must be examined to see if it contains
	an atom.

>>>>

In crystallography, a unit cell represents an entire lattice, displaying all the symmetries of a crystal except for the translations.  The entire lattice is generated by assembling all the translational repetitions of the unit cell.

@@

In order to measure a meaningful distance between two objects, the objects need to
be placed in a ”metric space”. For crystallographic unit cells, this will often be a
vector space amenable to the tools and techniques of
linear algebra, at least locally. Because six free parameters are needed to define a unit
cell, the space will need to be at least six-dimensional. Depending on
other criteria, more dimensions may be needed; gluing the edges of
a manifold generates the need for more dimensions. The dimensionality of a unit cell itself should be distinguished from the higher dimensions of the spaces in which it may be useful to embed the cell.

@@

	In working with a space in which there are 
	multiple symmetry-related occurrences of items of interest (atoms, molecules, or,
	in this case, unit cells), it is conventional to choose a fundamental
	region. ``A fundamental domain or fundamental region is a subset of the space which contains exactly one point from each of these orbits. It serves as a geometric realization for the abstract set of representatives of the orbits.'' \cite{enwiki:1028832752}. In a two-dimensional graph, it would often be chosen as the all-plus
	quadrant. In crystallography, it might be a unit cell, a
	particular asymmetric unit of a crystal, or even a molecule.

@@

	The obvious first step in finding the shortest distance between two
	lattices is to simply compute the Euclidean distance between
	them in the fundamental unit. That distance might not be the
	shortest that can be found, but no geodesic could 
	be longer. It makes a useful starting point. Call 
	this distance $d_0$.

@@

%\begin{figure}
		\includegraphics[width = 0.5\textwidth ]{4_3}
		\label{4_3}
%	\caption{}
%\end{figure}	
	It is clear that within the fundamental unit, ignoring all symmetry
	transforms and considering B and C, B is the atom closer to
	A. Draw a circle centered on A that touches B. We see that the
	circle crosses the boundary and a portion is outside of the
	fundamental unit. Any atom that is within that region outside the fundamental unit must be examined to see if it contains
	an atom.
